---
title: "VedicDateTime"
author: "Prajwal Patil"
output:
  rmdformats::readthedown:
    self_contained: true
    thumbnails: true
    lightbox: true
    gallery: false
    highlight: tango
  pdf_document:
    toc: true
    highlight: zenburn
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r, include = FALSE}
install.packages("swephR",repos = "https://CRAN.R-project.org/package=swephR")
library(swephR)
data(SE)
options(digits = 5)
```

```{r setup}
library(VedicDateTime)
```

# Gregorian to JD
Convert Gregorian date to Julian day number at 00:00 UTC
```{r}
gregorian_to_jd(17,6,2022) #In dd,mm,yyyy
```

# JD to Gregorian
Convert Julian day number to Gregorian date
```{r}
jd_to_gregorian(2459778)
```

# Sun's Longitude
Get Solar longitude for a given Julian day number.
```{r}
sun_longitude(2459778)
```

```{r}
sun_longitude(gregorian_to_jd(17,6,2022))
```

# Moon's Longitude
Get Lunar longitude for a given Julian day number.
```{r}
moon_longitude(2459778)
```

```{r}
moon_longitude(gregorian_to_jd(17,6,2022))
```

# Sunrise
Sunrise for a given date and place.
```{r}
jd <- 2459778 #Julian day number
place <- c(15.34, 75.13, +5.5) #Latitude, Longitude and timezone of the location
sunrise(jd,place)
```

```{r}
jd <- gregorian_to_jd(17,6,2022) #Julian day number
place <- c(15.34, 75.13, +5.5) #Latitude, Longitude and timezone of the location
sunrise(jd,place)
```

# Sunset
Sunset for a given date and place.
```{r}
jd <- 2459778 #Julian day number
place <- c(15.34, 75.13, +5.5) #Latitude, Longitude and timezone of the location
sunset(jd,place)
```

```{r}
jd <- gregorian_to_jd(17,6,2022) #Julian day number
place <- c(15.34, 75.13, +5.5) #Latitude, Longitude and timezone of the location
sunset(jd,place)
```


# Moonrise
Moonrise for a given date and place.
```{r}
jd <- 2459778 #Julian day number
place <- c(15.34, 75.13, +5.5) #Latitude, Longitude and timezone of the location
moonrise(jd,place)
```

```{r}
jd <- gregorian_to_jd(17,6,2022) #Julian day number
place <- c(15.34, 75.13, +5.5) #Latitude, Longitude and timezone of the location
moonrise(jd,place)
```


# Moonset
Moonset for a given date and place.
```{r}
jd <- 2459778 #Julian day number
place <- c(15.34, 75.13, +5.5) #Latitude, Longitude and timezone of the location
moonset(jd,place)
```

```{r}
jd <- gregorian_to_jd(17,6,2022) #Julian day number
place <- c(15.34, 75.13, +5.5) #Latitude, Longitude and timezone of the location
moonset(jd,place)
```

# Panchang
## Tithi 

Tithi for given date and place.
```{r}
jd <- 2459778 #Julian day number
place <- c(15.34, 75.13, +5.5) #Latitude, Longitude and timezone of the location
tithi(jd,place)
```

```{r}
tithi(gregorian_to_jd(17,6,2022),c(15.34, 75.13, +5.5))
```

### Tithi's name
Get name(s) of the Tithi for given Julian day number and place.

```{r}
jd <- 2459778 #Julian day number
place <- c(15.34, 75.13, +5.5)  #Latitude, Longitude and timezone of the location
get_tithi_name(jd,place)
```

```{r}
get_tithi_name(gregorian_to_jd(17,6,2022),c(15.34, 75.13, +5.5))
```
## Nakshatra 

Nakshatra for given date and place.
```{r}
jd <- 2459778 #Julian day number
place <- c(15.34, 75.13, +5.5)  #Latitude, Longitude and timezone of the location
nakshatra(jd,place)
```

```{r}
nakshatra(gregorian_to_jd(17,6,2022),c(15.34, 75.13, +5.5))
```

### Nakshatra's name
Get name(s) of the Nakshatra for given Julian day number and place.

```{r}
jd <- 2459778 #Julian day number
place <- c(15.34, 75.13, +5.5)  #Latitude, Longitude and timezone of the location
get_nakshatra_name(jd,place)
```

```{r}
get_nakshatra_name(gregorian_to_jd(17,6,2022),c(15.34, 75.13, +5.5))
```

## Yoga

Yoga for given date and place.
```{r}
jd <- 2459778 #Julian day number
place <- c(15.34, 75.13, +5.5)  #Latitude, Longitude and timezone of the location
yoga(jd,place)
```

```{r}
yoga(gregorian_to_jd(17,6,2022),c(15.34, 75.13, +5.5))
```

### Yoga's name
Get name(s) of the Yoga for given Julian day number and place.

```{r}
jd <- 2459778 #Julian day number
place <- c(15.34, 75.13, +5.5) #Latitude, Longitude and timezone of the location
get_yoga_name(jd,place)
```

```{r}
get_yoga_name(gregorian_to_jd(17,6,2022),c(15.34, 75.13, +5.5))
```

## Karana

Karana for given date and place.
```{r}
jd <- 2459778 #Julian day number
place <- c(15.34, 75.13, +5.5) #Latitude, Longitude and timezone of the location
karana(jd,place)
```

```{r}
karana(gregorian_to_jd(17,6,2022),c(15.34, 75.13, +5.5))
```

### Karana's name
Get name(s) of the Karana for given Julian day number and place.

```{r}
jd <- 2459778 #Julian day number
place <- c(15.34, 75.13, +5.5) #Latitude, Longitude and timezone of the location
get_karana_name(jd,place)
```

```{r}
get_karana_name(gregorian_to_jd(17,6,2022),c(15.34, 75.13, +5.5))
```

# Vaara
Vaara for a given Julian day number

```{r}
vaara(2459778)
```

```{r}
vaara(gregorian_to_jd(6,8,2022))
```

## Vaara's name

Get name of the Vaara for given Julian day number.

```{r}
get_vaara_name(2459778)
```

```{r}
get_vaara_name(gregorian_to_jd(6,8,2022))
```

# Masa
Masa for a given place and time.
```{r}
jd <- 2459778 #Julian day number
place <- c(15.34, 75.13, +5.5) #Latitude, Longitude and timezone of the location
masa(jd,place)
```

```{r}
masa(gregorian_to_jd(17,6,2022),c(15.34, 75.13, +5.5))
```

## Masa's name
Get name of the Masa for given Julian day number and place.
```{r}
jd <- 2459778 #Julian day number
place <- c(15.34, 75.13, +5.5) #Latitude, Longitude and timezone of the location
get_masa_name(jd,place)
```

```{r}
get_masa_name(gregorian_to_jd(17,6,2022),c(15.34, 75.13, +5.5))
```

# Ritu
Returns the number associated with Ritu from a Masa.

```{r}
masa_num <- masa(gregorian_to_jd(17,6,2022),c(15.34, 75.13, +5.5))[1]
ritu(masa_num)
```

## Ritu's name
Returns Ritu's name from a Masa.

```{r}
masa_num <- masa(gregorian_to_jd(17,6,2022),c(15.34, 75.13, +5.5))[1]
get_ritu_name(masa_num)
```

# Samvatsara

Returns number associated with the name of the Shaka Samvatsar for a given Julian day number and maasa number.
```{r}
jd <- gregorian_to_jd(17,6,2022) #Julian day number
masa_num <- masa(gregorian_to_jd(17,6,2022),c(15.34, 75.13, +5.5))[1] #Number associated with the masa
samvatsara(jd,masa_num)
```

## Samvatsara's name

Returns the name of the Shaka Samvatsar for a given Julian day number and maasa number.
```{r}
jd <- gregorian_to_jd(17,6,2022) #Julian day number
masa_num <- masa(gregorian_to_jd(17,6,2022),c(15.34, 75.13, +5.5))[1] #Number associated with the masa
get_samvatsara_name(jd,masa_num)
```

# Raasi
Raasi(Sun-sign) for a given Julian day number
```{r}
jd <- gregorian_to_jd(17,6,2022) #Julian day number
raasi(jd)
```

## Raasi's name
Gives name of the Raasi(Sun-sign) for a given Julian day number
```{r}
jd <- gregorian_to_jd(17,6,2022) #Julian day number
get_raasi_name(jd)
```

# Moon-sign
Moonsign for a given Julian day number
```{r}
jd <- gregorian_to_jd(17,6,2022) #Julian day number
moonsign(jd)
```

## Moonsign's name
Gives name of the moonsign for a given Julian day number
```{r}
jd <- gregorian_to_jd(17,6,2022) #Julian day number
get_moonsign_name(jd)
```
